Introduction to Market Research

### 2021-12-15 kampus merdeka/market_riset/market_riset.Rmd
new

```{r,echo=FALSE}
nomnoml::nomnoml("
                 [Masalah] -> [Butuh Data]
                 [Butuh Data] -> [Ada data sekunder?]
                 [Ada data sekunder?] -> [Ada]
                 [Ada data sekunder?] -> [Tidak ada]
                 [Tidak ada] -> [Cari data primer]
                 [Ada] -> [Cek karakteristik]
                 [Cek karakteristik] -> [Masih relevan?]
                 [Masih relevan?] -> [Ya]
                 [Masih relevan?] -> [Tidak]
                 [Tidak] -> [Cari data primer]
                 [Ya] -> [Pakai data sekunder]
                 ")
```

>>>>

```{r,include=FALSE}
nomnoml::nomnoml("
                 [Masalah] -> [Butuh Data]
                 [Butuh Data] -> [Ada data sekunder?]
                 [Ada data sekunder?] -> [Ada]
                 [Ada data sekunder?] -> [Tidak ada]
                 [Tidak ada] -> [Cari data primer]
                 [Ada] -> [Cek karakteristik]
                 [Cek karakteristik] -> [Masih relevan?]
                 [Masih relevan?] -> [Ya]
                 [Masih relevan?] -> [Tidak]
                 [Tidak] -> [Cari data primer]
                 [Ya] -> [Pakai data sekunder]
                 ",
		 "ikanx.png",900,400
		)
```

```{r,echo=FALSE}
knitr::include_graphics("ikanx.png")
```
